\chapter{Conclusion}
% Conclusion -- summary, discussions, comments, etc.  
% (Please, do not write any sentence starting with "This summer practice was very useful for me")
All in all, I can say that my internship in there were significantly more 
fruitful than my previous internshipt, mostly because the stakes were just 
higher. However, the company didn't really adopt agile or any other popular 
software development methodology. I believe that they have just came up 
with their own method where it doesn't necessarily pressure the staff 
while still making a healthy balance of speed and quality.
\section{Methodologies and Strategies Used in the Company}
Before I have started my time there, the company was already having decent 
amount of meetings. However, most of them were kinda forced due to pandemic. 
After proposing a daily meeting which would be similar to scrums that are 
commonly seen on Agile methodology, Mustafa fortunately agreed. We had 
brief meetings daily to summarize our work and share our daily plan. These 
meeetings usually took about 10-15 minutes.
\par
Although some of it depended on customer's preferences, the company mostly 
uses TFS, Azure DevOps to keep track of work done by its staff. For version 
control we have used Git which was quite useful. I kept track of my own 
daily work in a sheet and made sure that I had regular commits on the 
repository I was contributing in.
\par
I have shared my tendencies when it comes to requirements and actively 
communicated about the needs and constraints whenever I has demanded a work. 
In that regarding although documentation was not done thoroughly, I can still 
say that I was given enough instructions when I was expected certain work. 
When I felt stuck, I would contact either Derviş or Koray, but I was not 
limited to work with them alone. My peer Şahin would also join me on debugging 
when he was available. When it comes to picking a solution for certain tasks 
such as forms, Emin would share what he uses on their projects etc.
