\chapter{Introduction}
% Introduction to the report -- organization, project, your participation, 
% outline of the report, etc.

This document contains information regarding my internship in Siren Bilisim 
on summer of 2021. The document will consist of information about the 
organization, project I have worked on and my role in the project. 
Although its development process isn't perfecly aligned with software 
development lifecycle, the details regarding the project, namely PGMaster, 
will be organized as following:

\begin{itemize}
    \item \textbf{Analysis:} In this section, I will be explaining the effort 
    put into understanding and determining the requirements for the software.
    \item \textbf{Design:} In this section, the design choices that were made 
    in accordance with the requirements will be demonstrated.
    \item \textbf{Implementation:} The development of the software in somewhat 
    intertwined with the prior phases. However, explanations regarding the 
    implementation specifically will be included in this section.
    \item \textbf{Testing:} This software's implementation involves thorough 
    testing of its different modules. In terms of the timeline, the testing is 
    not necessarily performed \textit{after} implementation. Information 
    regarding testing will still be written in this section of the document 
    for sake of sticking with the outline demanded by the department.
\end{itemize}

\par

The internship is performed in Siren Bilisim under the supervision of Koray 
Kocamaz. During that time, I have been mainly involved in web development 
activities. Before the internship, I have had developed various applications 
that utilizes web technologies. During the internship, I had chance to learn 
more about front-end development on top of back-end. The project mainly involves 
active participation of three developers. While I have performed my day-to-day 
development activities under supervision of Koray, the team member that I 
worked with the most was Derviş Mahmutoğlu from HAVELSAN. In that regard, I 
could partially claim that my internship project included the contribution of 
multiple organizations although HAVELSAN itself is not officially involved.
\par
Although my involvement in PGMaster was not limited to the front-end, majority 
of the source code I have written would allow users interact with the 
underlying system. Due to that, I will be sharing extensive demonstration of 
the user interfaces.
\par
On top of web development, the project revolves around databases, containers, 
and clusters. Domain knowledge about these entities have been also learned 
during this internship. I will be mentioning them in detail within relevant 
sections of the report.